\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-09 doc/paper.tex
Talk abou how index number breeds confusion. Closes #144.

	\subsection{Study Limitations} Though we did not start the study by telling
	that the data source came from Enron, two users studied the file names to
	deduce its roots in finance, if not Enron itself. Because of these notorious
	connotations, then, they might have been inclined from this information to
	orient their exploration around finance-related functions, potentially limiting
	their findings or perceived users for the tool. However, one participant also
	said that, without this essential context, they could not have intelligently
	explored a dataset in the first place. Comments like these point out the
	trade-offs of unguided exploration, too: though it might not restrict them to a
	single purpose, it might, at the same time, not afford them any mindset at all
	with which to interpret the data. \par

@@

	We realized early that some of the popular functions would have thousands of
	variations in large datasets, and showing all of these variations at once would
	hopelessly overwhelm the user. We therefore made a number of choices, such as
	the expansion arrows and the use of generic types in place of specific
	primitive values, that would reduce the variation to something more manageable.

	Nevertheless, during the user study, P3 remarked that they specifically avoided
	the most popular functions, anticipating a flood of nodes from which they could
	salvage nothing interesting. P2 corroborated this by explaining how they
	gravitated toward exploring specific examples in particular value nodes over
	navigating the full, crowded tree, but they complicate it further by also
	saying that the tool at its best when it shows either every possibility of an
	argument side-by-side (for comparison) or nothing on that branch at all, a
	balance that is hard to strike with node-dense trees.

	A threat to our goals, then, arises from the problem of too much data,
	particularly in the popular functions, like SUM and IF. Despite our
	precautions, balancing the desire to show every single possibility of design
	with the desire not to overwhelm remains a challenge. \par

>>>>

	\subsection{Study Limitations} \label{subsec:studylimitations} Though we did not start the study by telling
	that the data source came from Enron, two users studied the file names to
	deduce its roots in finance, if not Enron itself. Because of these notorious
	connotations, then, they might have been inclined from this information to
	orient their exploration around finance-related functions, potentially limiting
	their findings or perceived users for the tool. However, one participant also
	said that, without this essential context, they could not have intelligently
	explored a dataset in the first place. Comments like these point out the
	trade-offs of unguided exploration, too: though it might not restrict them to a
	single purpose, it might, at the same time, not afford them any mindset at all
	with which to interpret the data. \par

@@

	A threat to our goals arises from the problem of too much data,
	particularly in the popular functions, like SUM and IF. We realized early that
	these functions would overwhelm the user with options in large datasets, so we
	included features, such as the expansion arrows and the use of generic types
	instead of values, that would manage the variation. Nevertheless, P3 remarked
	that they specifically avoided the most popular functions, anticipating a flood
	of nodes from which they could salvage nothing interesting. P2 corroborated
	this by explaining how they gravitated toward exploring specific examples in
	particular value nodes over navigating the full, crowded tree, but they also
	said that the tool at its best when it compares either every possibility of an
	argument side-by-side or nothing on that branch at all. Despite our
	precautions, balancing the desire to show a lot with the desire not to
	overwhelm remains a challenge. \par

	Some visual cues turned out to be more confusing than helpful, such as
	the index number on each argument node. As discussed in Section~\ref{subsec:studylimitations},
	users often mistook it for other features, like total number of arguments in the
	function. Though we kept this feature present for all studies, future versions
	of the tool would refine features like this to reduce confusion.
